\documentclass[10.5pt,a4paper]{article}

\usepackage[left=0.65in,right=0.65in,top=0.55in,bottom=0.55in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{newtxtext,newtxmath}
\usepackage{microtype}

\setlength{\parindent}{0pt}
\setlength{\emergencystretch}{2em}
\pagestyle{empty}
\setlist[itemize]{leftmargin=*,itemsep=0.1em,topsep=0.1em}

\newcommand{\sectionline}[1]{
\vspace{0.45em}
{\normalsize \textbf{\MakeUppercase{#1}}}\\[-0.45em]
\rule{\textwidth}{0.5pt}
\vspace{0.15em}
}

\begin{document}

\begin{center}
{\Large \textbf{Vibhu Gautam}}\\
Paonta Sahib, India \;|\; +91-9317860077 \;|\;
\href{mailto:vibhu.gautam7@gmail.com}{vibhu.gautam7@gmail.com} \;|\;
\href{https://www.linkedin.com/in/vibhugautam7}{linkedin.com/in/vibhugautam7}
\end{center}

\vspace{-0.5em}

\sectionline{Profile}
People Analytics \& Data AI Leader with 12+ years of experience across Nestlé, McKinsey, BCG, Micron, and academia. Built enterprise workforce analytics, predictive models, and cloud data platforms using Python, Snowflake, Azure, APIs, and BI tools to support global HR and business decision-making.

\sectionline{Core Skills}
\textbf{People Analytics:} Attrition Modeling, Workforce Planning, Payroll Analytics, Sentiment Analysis \\
\textbf{Platforms:} Snowflake, Azure (ADF, ADLS, Synapse, API Management), AWS \\
\textbf{Technical:} Python, SQL, Pandas, NumPy, TensorFlow, FastAPI \\
\textbf{Visualization:} Power BI, Streamlit, Tableau

\sectionline{Experience}

\textbf{Professor of Practice -- Computer Science} \hfill Aug 2024 -- Present \\
\textit{UPES, Dehradun}
\begin{itemize}
\item Delivered courses in Data Architecture, Snowflake, and Big Data through project-based learning.
\item Mentored students on end-to-end analytics system design, including pipelines, APIs, and cloud deployment.
\end{itemize}

\textbf{Innovation Lead -- Data \& AI (Global People Analytics)} \hfill Mar 2023 -- Aug 2024 \\
\textit{Nestlé HQ, Gurugram}
\begin{itemize}
\item Delivered workforce intelligence solutions for the Global People Analytics team supporting enterprise HR decisions.
\item Built analytics products for attrition, payroll insights, and workforce planning using Azure-based data platforms.
\item Improved governance and data quality practices to strengthen reliability and scale of analytics delivery.
\end{itemize}

\textbf{Data Scientist -- Full Stack (People Analytics)} \hfill Aug 2021 -- Apr 2023 \\
\textit{Nestlé UK, York}
\begin{itemize}
\item Developed end-to-end analytics solutions spanning ingestion, modeling, APIs, and dashboards.
\item Built predictive models for attrition and workforce behavior to support proactive HR decision-making.
\item Delivered dashboards for workforce planning and employee engagement insights.
\end{itemize}

\textbf{Marie-Curie Early Stage Researcher} \hfill May 2019 -- Aug 2021 \\
\textit{University of York}
\begin{itemize}
\item Developed Bayesian AI models for uncertainty-aware decision systems and predictive analytics.
\item Published research in SafeAI 2021 and EAI 2021 on autonomous systems and clinical conversational AI.
\end{itemize}

\textbf{Data Scientist -- Data Platforms} \hfill Aug 2017 -- Nov 2018 \\
\textit{Micron, Japan}
\begin{itemize}
\item Built Spark-based pipelines and predictive models to improve yield and operational decision-making.
\item Integrated manufacturing and enterprise datasets to identify drivers of productivity and throughput.
\end{itemize}

\textbf{Earlier Experience} \hfill 2012 -- 2016 \\
\textit{Boston Consulting Group (BCG); McKinsey \& Company}
\begin{itemize}
\item Built analytics tools for workforce strategy, market assessment, productivity benchmarking, and functional efficiency.
\item Supported HR and enterprise decision-making through data models on talent, cost, and operational performance.
\end{itemize}

\sectionline{Selected Work}
\textbf{Global People Analytics Platform -- Nestlé:} Built workforce analytics solutions supporting enterprise HR decision-making. \\
\textbf{Enterprise Analytics Platform -- Nestlé HQ:} Designed scalable Azure-based analytics architecture with CI/CD pipelines.

\sectionline{Education}
M.Sc. Computer Science, University of Southampton \hfill 2009 -- 2010 \\
B.Tech. Electronics \& Communication, Chitkara University \hfill 2005 -- 2009

\sectionline{Certifications \& Publications}
Machine Learning \& AI, upGrad \hfill 2019 \\
Data Science for IoT, University of Oxford \hfill 2017 \\
References: Available on request

\end{document}